\documentclass[12pt,a4paper]{article}

\begin{document}

\title{\textbf{Abstract}}
\author{
  Alan Joy \and
  Deepa Mary Jose \and
  Devananda Sumod \and
  S V Anupama \and
  Jairaj
}
\date{}
\maketitle

\begin{abstract}
The Logistics and Delivery Management System is a Java Swing and SQLite-based application designed to simulate the operations of a logistics network. The system manages order placement, shipment tracking, delivery scheduling, warehouse inventory, and vehicle allocation. It supports multiple user roles including administrators, customers, delivery agents, and warehouse managers, each with role-specific functions such as shipment requests, product purchases, vehicle booking, payment processing, vendor management, and delivery monitoring.

The architecture follows object-oriented programming principles, employing classes, inheritance, and abstraction to model real-world logistics entities such as products, vehicles, warehouses, and delivery agents. Database integration enables storage and retrieval of user information, orders, and warehouse data, while the GUI provides interactive dashboards tailored for each role.

Key features include shipment requests with warehouse queuing, purchase flows with retailer selection, vehicle transport scheduling, delivery status updates, and cash-on-delivery payments. Administrators oversee vendor and vehicle management, traffic monitoring, and user concerns, while agents and warehouse managers handle assigned deliveries and stock updates.

Although limited to desktop simulation without live tracking or online payments, the system provides a practical demonstration of logistics workflows while reinforcing academic concepts in object-oriented programming, GUI development, and database management.
\end{abstract}

\end{document}
