% Logistics_and_Delivery_Management_System.tex
\documentclass[12pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}            % better paragraph spacing
\usepackage{enumitem}           % control lists
\usepackage{titlesec}           % control heading spacing
\usepackage{hyperref}           % clickable links and metadata
\usepackage{graphicx}           % if you want to add images/diagrams
\usepackage{fancyhdr}           % header/footer
\usepackage{caption}

% Document metadata
\title{Logistics and Delivery Management System}
\author{GROUP 8 \\ S3 CSE B2 \\ CET, TVM}
\date{\today}

% Heading spacing adjustments
\titlespacing*{\section}{0pt}{12pt}{6pt}
\titlespacing*{\subsection}{0pt}{10pt}{4pt}

% Header / Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Logistics and Delivery Management System}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Line spacing
\setstretch{1.15}

\begin{document}

% Cover page
\begin{titlepage}
  \centering
  \vspace*{2.0cm}
  {\LARGE\bfseries Logistics and Delivery Management System \par}
  \vspace{1.5cm}
  {\large \textbf{Object Oriented Programming Project Abstract } \par}
  \vspace{2.0cm}
  {\large \textbf{Prepared by:} \\[6pt] Alan Joy, Deepa Mary Jose, Deva Nanda Sumod, Jairaj R, S V Anupama \\[6pt] S3 CSE B2  \\[6pt] CET, TVM \par}
  \vfill
  {\large Date: \today \par}
  \vspace{1.5cm}
\end{titlepage}

\tableofcontents
\thispagestyle{empty}
\clearpage

\section{Introduction}
The \textbf{Logistics and Delivery Management System} is a Java Swing and SQLite-based project designed to manage order placement, shipment tracking, delivery scheduling, and warehouse inventory.

It simulates real-world logistics operations using object-oriented programming (OOP) concepts such as classes, inheritance, and abstraction, along with database handling.

The system includes modules for Users (Admin, Customer, Delivery Agent, Warehouse Manager), Vehicles, and Orders, with features such as:
\begin{itemize}[noitemsep]
  \item Order placement and tracking
  \item Delivery scheduling
  \item Route management
  \item Warehouse inventory monitoring
  \item Billing and payment
\end{itemize}

\section{System Features}

\subsection{User Operations}
\begin{itemize}[noitemsep]
  \item Request shipment from source to destination.
  \item Purchase products from available retailers listed in the database.
  \item Request a vehicle for transportation.
  \item Get updates for shipments, purchases, and transportation.
  \item Make payments to delivery agents securely.
\end{itemize}

\subsection{Admin Responsibilities}
\begin{itemize}[noitemsep]
  \item Add vendors, warehouses, and vehicles (with validation through document verification).
  \item Monitor delivery traffic and detect issues such as route overloads or lack of agents.
  \item Address user concerns including complaints, suggestions, and technical issues.
\end{itemize}

\subsection{Delivery Agent Features}
\begin{itemize}[noitemsep]
  \item View assigned deliveries on personal dashboard.
  \item Update status of deliveries (Picked up, In Warehouse, Out for Delivery, Delivered).
  \item Accept/reject delivery requests (based on distance, workload).
  \item Manage personal delivery history (past completed deliveries).
  \item Receive payment confirmation once user completes transaction.
\end{itemize}

\subsection{Warehouse Manager Features}
\begin{itemize}[noitemsep]
  \item Dashboard showing current warehouse stock and inventory summary.
  \item Manage queue of products waiting for delivery (FIFO scheduling).
  \item Assign items to delivery agents for outbound shipments.
  \item Track incoming products arriving at the warehouse.
  \item Maintain reports on warehouse capacity and performance.
\end{itemize}

\section{GUI Design}
The graphical user interface is built using \textbf{Java Swing}, with different views for each user role:

\begin{enumerate}
  \item \textbf{Login Page} – Role-based login (User, Admin, Delivery Agent, Warehouse Manager).
  \item \textbf{User Dashboard} – Shows request history in charts, and a navigation bar for shipment, purchase, transport, and payment.
  \item \textbf{Admin Dashboard} – Charts and tables summarizing system health: active orders, pending deliveries, available vehicles, and warehouse stock. Navigation bar provides access to vendor, warehouse, vehicle, and traffic management modules.
  \item \textbf{Delivery Agent / Warehouse Manager Dashboard} – Delivery agents see a list of past and ongoing deliveries; warehouse managers see stock summaries, pending shipments, and available delivery agents.
\end{enumerate}

\section{Interface / Abstraction of Features}

\subsection{Shipment of Product}
\textbf{Class Components:} Product, DeliveryAgent, Warehouse, Vehicle

\textbf{Workflow:}
\begin{enumerate}[leftmargin=*,noitemsep]
  \item User requests shipment \(\rightarrow\) System finds available agent.
  \item Match based on package size/type, vehicle availability, and proximity.
  \item Agent status updated to \textit{Working}.
  \item Product queued in warehouse (FIFO).
  \item Assigned agent delivers to destination.
\end{enumerate}

\textit{Optional: Direct pickup-to-destination if feasible.}

\subsection{Purchase of Product}
\textbf{Class Components:} Product, Retailer, DeliveryAgent, Vehicle

\textbf{Workflow:}
\begin{enumerate}[leftmargin=*,noitemsep]
  \item User searches for a product.
  \item System filters retailers by distance, price, and availability.
  \item Shipment flow applied directly (without warehouse).
\end{enumerate}

\subsection{Vehicle for Transportation}
\textbf{Class Components:} Vehicle, Driver, TransportationRequest

\textbf{Workflow:}
\begin{enumerate}[leftmargin=*,noitemsep]
  \item User requests vehicle with pickup/drop details.
  \item Database searched for available vehicles.
  \item Suggested options displayed to user with driver details.
  \item Vehicle object created and location updates simulated every 5 minutes.
\end{enumerate}

\subsection{Payment Module}
\textbf{Class Components:} Payment (abstract), CardPayment, UPIPayment, WalletPayment, Invoice

\textbf{Workflow:}
\begin{enumerate}[leftmargin=*,noitemsep]
  \item Generate invoice object with order, agent, and cost details.
  \item User chooses payment method (Card/UPI/Net Banking/Wallet).
  \item Simulated payment gateway (recorded in SQLite).
  \item Update invoice and notify agent.
  \item Maintain payment history in dashboard.
\end{enumerate}

\subsection{Tracking Module}
\textbf{Class Components:} Tracking, Order, Vehicle, DeliveryAgent

\textbf{Workflow:}
\begin{enumerate}[leftmargin=*,noitemsep]
  \item System generates Tracking ID for each request.
  \item Agent’s location and order status (Picked Up, In Warehouse, Out for Delivery, Delivered) updated in DB.
  \item User dashboard shows order progress via progress bar or map-like view.
  \item Admin dashboard aggregates all deliveries, highlighting delayed shipments.
  \item Location updates simulated periodically in SQLite.
\end{enumerate}

\section{Common Features}
All roles in the system share \textbf{personal information attributes} such as name, contact details, and login credentials, ensuring a uniform data structure.

\section{Conclusion}
The Logistics and Delivery Management System integrates \textbf{OOP concepts, Swing-based GUI design, and SQLite database handling} to provide a complete solution for shipment requests, product purchases, transportation, payments, and tracking. It acts as a \textbf{mini-simulation of real-world logistics operations}.

\end{document}
